TITLE

### 2021-02-23 outputs/Paper.Rmd
update

```
# Discussion

>>>>

### restaurant type by regions

```{r restaurant_type, echo=FALSE}

library(viridis)

# Treated group
rt1<-
  ggplot(treated_data, aes(fill= Q3, x= Q2)) +
  geom_bar(position="stack", stat="count")+
    ggtitle("Treated Group: Restaurant Types in different regions") +
    xlab("Regions")+
    ylab("Count of Numbers")+
    theme_grey()

rt1<- rt1 + guides(fill=guide_legend(title="Types")) # change the Legend title

# Control group
rt2<-
  ggplot(control_data, aes(fill= Q3, x= Q2)) +
  geom_bar(position="stack", stat="count")+
    ggtitle("Control Group: Restaurant Types in different regions") +
    xlab("Regions")+
    ylab("Count of Numbers")+
    theme_grey()

rt2<- rt2 + guides(fill=guide_legend(title="Types")) # change the Legend title 
# combine two diagram in one graph
ggarrange(
  rt1, rt2, 
  ncol = 2, nrow = 1,
  vjust = 1,
  widths = c(2, 2),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

### Flex and fiexed cost changes

```{r felx_fix, echo=FALSE, fig.width=10, fig.height=4}

# Treated group

# Fixed costs 
fixc1<-
  ggplot(treated_data, aes(fill= Q11, x=Q11)) +
  geom_bar(stat="count", width = 0.5)+
    ggtitle("Fixed costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# flex cost
flexc1<-
    ggplot(treated_data, aes(fill= Q12, x=Q12)) +
    geom_bar(stat="count", width = 0.5)+
    ggtitle("Treated Group: Flexible costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# Control group
fixc2<-
  ggplot(control_data, aes(fill= Q11, x=Q11)) +
  geom_bar(stat="count", width = 0.5)+
    ggtitle("Fixed costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

fixc2<- fixc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# flex cost
flexc2<-
    ggplot(control_data, aes(fill= Q12, x=Q12)) +
    geom_bar(stat="count", width = 0.5)+
    ggtitle("Control Group: Flexible costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

flexc2<- flexc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# combine two diagram in one graph
ggarrange(
  flexc1,fixc1,flexc2, fixc2,
  ncol = 2, nrow = 2,
  vjust = 1,
  widths = c(2, 2),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

### Distribution average employee salary
```{r salary_distribution, echo=FALSE, fig.width=10, fig.height=4}
library(ggthemes)
# Treated group
s1<-
  ggplot(treated_data, aes(x = Q2, y= Q9)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="Salary Distributions in Treated Group", x="Regions", y="Hourly rate")+
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ # add dots
  theme_economist()

# Control group
s2<-
  ggplot(control_data, aes(x = Q2, y= Q9)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="Salary Distributions in Control Group", x="Regions", y="Hourly rate")+
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ #add dots
  theme_economist()

# combine two diagram in one graph

library(ggpubr)
ggarrange(
  s1, s2, 
  ncol = 2, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )

### correlation matrix
```{r correlation, echo=FALSE, fig.width=10, fig.height=4}

# Discussion
